---
title: "About package"
author: "Kato Akiru"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{About package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
if(!require(nanoidr)) stop()
if(!require(dqrng)) stop()
```

## What is {nanoidr}?

[ai/nanoid](https://github.com/ai/nanoid) is a tiny (137 bytes), secure, URL-friendly, unique string ID generator for JavaScript. The {nanoidr} package is a pseudo R wrapper of NanoID library running on [V8 for R](https://github.com/jeroen/V8).

## Disclaimers

> The original NanoID library generates random strings with window.crypto.getRandomValues on client side environment, however, the V8 environment provides no crypto object. Because of this, {nanoidr} package replaces that function with a simple wrapper of openssl::rand_bytes().

So that V8 environment has no crypto API, behaivors between {nanoidr} and the original NanoID library may be different in details. See also [Generating Secure Random Numbers in R](https://cran.r-project.org/web/packages/openssl/vignettes/secure_rng.html) for more details of `openssl::rand_bytes()`.

## Related repositories

- [ai/nanoid](https://github.com/ai/nanoid) The original NanoID library.
- [CyberAP/nanoid-dictionary](https://github.com/CyberAP/nanoid-dictionary) Predefined character sets to use with nanoid.
- [y-gagar1n/nanoid-good](https://github.com/y-gagar1n/nanoid-good) Obscene words filter for nanoid.
- [jeroen/V8](https://github.com/jeroen/V8) Embedded JavaScript Engine for R.

## How to use

### Common use case

```{r}
nano <- nanoidr::nanoid()
nano$generate() # the simplest use case
nano$generate(size = 13L, dict = "numbers") # generate from built in pattern
nano$generate(size = 16L, dict = "You can use any strings as dictionary!!")
nano$generate(size = 16L, dict = "マルチバイト文字を使っても動作します", init.locales = "ja")
nano$nonsecure(size = 27L) # use faster but non-secure version
```

### Using custom random bytes generator

```{r}
myRndBytesFunc <- function(size) {
  sapply(1:size, function(i){ abs(floor(dqrng::dqrnorm(1, 0, 64))) })
}
nano$format(size = 38L, use_func = "myRndBytesFunc")
```

### Customizing and reusing V8 context

``` R
nano <- nanoidr::nanoid()
mycontext <- nano$ctx
mycontext$source("another_awesome_source.js")
nano2 <- nanoidr::nanoid(ctx = mycontext)
```


