---
title: "about"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{about}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(nanoidr)
library(dqrng)
```

## What is {nanoidr}?

[ai/nanoid](https://github.com/ai/nanoid) is a tiny (137 bytes), secure, URL-friendly, unique string ID generator for JavaScript. The {nanoidr} package is a simple wrapper of NanoID library running on [V8](https://github.com/jeroen/V8).

**Related repositories**

- [ai/nanoid](https://github.com/ai/nanoid) NanoID
- [CyberAP/nanoid-dictionary](https://github.com/CyberAP/nanoid-dictionary) Predefined character sets to use with nanoid.
- [y-gagar1n/nanoid-good](https://github.com/y-gagar1n/nanoid-good) Obscene words filter for nanoid.
- [jeroen/V8](https://github.com/jeroen/V8) Embedded JavaScript Engine for R.

## How to use

Common use case

```{r}
nano <- nanoidr::nanoid()
nano$generate() # the simplest use case
nano$generate(size = 13L, dict = "numbers") # generate from built in pattern
nano$generate(size = 16L, dict = "You can use any strings as dictionary!!")
nano$generate(size = 16L, dict = "マルチバイト文字を使っても動作します", init.locales = "ja")
nano$nonsecure(size = 27L) # use faster but non-secure version
```

Use custom random bytes generator

```{r}
myRndBytesFunc <- function(size) {
  sapply(1:size, function(i){ floor(dqrng::dqrnorm(1, 3, i)) })
}
nano$format(size = 38L, use_func = "myRndBytesFunc")
```

